Learning CNN filters from user-drawn image markers for coconut-tree image classification

### 2020-07-23 main.tex
plot of increasing train set size

@@

\definecolor{navy}{RGB}{0,0,137}
\definecolor{tealDeer}{RGB}{148,232,180}
\definecolor{dodgerBlue}{RGB}{18,161,255}
\definecolor{citrine}{RGB}{230, 194, 8}
\definecolor{violet}{RGB}{112,5,164}
\definecolor{navyPurple}{RGB}{172,86,253}
\definecolor{heliotrope}{RGB}{236,93,253}

@@

\begin{table}[!t]
  \begin{center}
  \begin{tabular}{|l|c|c|c|}
  \hline
   Method & Precision & Recall & F-score \\
  \hline\hline
    FLIM+MLP & $0.894 \pm 0.006$ & $0.888 \pm 0.009$ & $0.890 \pm 0.008$\\
    FLIM-FT+MLP & $0.888 \pm 0.001$ & $0.878\pm 0.001$ & $0.881 \pm 0.001$ \\
    VGG-FT & $0.884 \pm 0.003$ & $0.877 \pm 0.006$ & $0.879 \pm 0.005 $ \\
  \hline
  \end{tabular}
  \end{center}

\caption{Mean and standard deviation of precision, recall, and f-score for each method: a feature extractor with a classifier with a larger train set.}
  \label{tab:results-with-1200-images}
\end{table}

>>>>

\usepackage{pgfplots,filecontents}

@@

\definecolor{navy}{RGB}{0,0,137}
\definecolor{tealDeer}{RGB}{148,232,180}
\definecolor{dodgerBlue}{RGB}{18,161,255}
\definecolor{citrine}{RGB}{230, 194, 8}
\definecolor{violet}{RGB}{112,5,164}
\definecolor{navyPurple}{RGB}{172,86,253}
\definecolor{heliotrope}{RGB}{236,93,253}
\definecolor{pink}{RGB}{250,38,160}

@@

\begin{comment}
  \begin{table}[!t]
  \begin{center}
  \begin{tabular}{|l|c|c|c|}
  \hline
   Method & Precision & Recall & F-score \\
  \hline\hline
    FLIM+MLP & $0.894 \pm 0.006$ & $0.888 \pm 0.009$ & $0.890 \pm 0.008$\\
    FLIM-FT+MLP & $0.888 \pm 0.001$ & $0.878\pm 0.001$ & $0.881 \pm 0.001$ \\
    VGG-FT & $0.884 \pm 0.003$ & $0.877 \pm 0.006$ & $0.879 \pm 0.005 $ \\
  \hline
  \end{tabular}
  \end{center}
  \caption{Mean and standard deviation of precision, recall, and f-score for each method: a feature extractor with a classifier with a larger train set.}
    \label{tab:results-with-1200-images}
  \end{table}
\end{comment}

\begin{figure}
\begin{tikzpicture}
  \begin{axis}[
    /pgf/number format/set thousands separator = {},
    xlabel = Train set size,
    ylabel = f-score,
    xmin=300, xmax=1200,
    grid=major,
    grid style=dashed,
    xtick={300,450, 600, 750, 900, 1050, 1200},
    legend style={nodes={scale=0.65, transform shape}},
    legend pos=south east
    ]
    \addplot table[x index=0,y index=1,header=false] {data/data.dat};
    \addlegendentry{FLIM+MLP}

    \addplot  table[x index=0,y index=2,header=false] {data/data.dat};
    \addlegendentry{FLIM-FT+MLP}

    \addplot  table[x index=0,y index=3,header=false] {data/data.dat};
    \addlegendentry{VGG-FT}

    \addplot table[x index=0,y index=4,header=false] {data/data.dat};
    \addlegendentry{CL+MLP}

    \legend{FLIM+MLP,FLIM-FT+MLP,VGG-FT,CL+MLP}

  \end{axis}
\end{tikzpicture}
\caption{Graph showing the impact of training set size on quantitative results. FLIM+MLP feature extractor was trained only with four images, and the remaining training set was used to train the MLP classifier.}
\end{figure}
